Proportional multi-state multiple-cohort life table model

### 2018-04-13 MSLT/MSLTdoc.Rmd
Added loop to generate graphs

```{r, echo=FALSE}
###TO DO: loops for sex, cause and measure and interpolation of rates, care with interpolating rates, need to convert to log for interpolation using cubic spline. 
#FOR NOW THE CODE FOR GRAPH IS repetitive
####################MORTALITY RATES ALL CAUSE PER ONE

###############################Mortality rates###################################################################

##Select data from data frames for all cause mortality males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause mortality rates males 
mx_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality rate")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Mortality rates difference males") +
  theme_classic()

print(mx_plot_compare_male)

##Select data from data frames for all cause mortality females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause mortality rates males 
mx_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality rate")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Mortality rates difference females") +
  theme_classic()

print(mx_plot_compare_female)

#############YLD RATES ALL CAUSE PER ONE

##################################yld rates all cause############################################################

##Select data from data frames for all cause yld rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "all causes" & measure == "ylds (years lived with disability)") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "all causes" & measure == "ylds (years lived with disability)") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause yld rates males 
totalyld_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Total YLDs rate")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Total YLDs rates difference males") +
  theme_classic()

print(totalyld_plot_compare_male)

##Select data from data frames for all cause yld females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "all causes" & measure == "ylds (years lived with disability)") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "all causes" & measure == "ylds (years lived with disability)") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause yld rates females 
totalyld_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Total YLDs rate")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Total YLDs rates difference females") +
  theme_classic()

print(totalyld_plot_compare_female)

################IHD
##############################Mortality rate ihd #############################################################

##Select data from data frames for ihd yld rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "ischemic heart disease" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "ischemic heart disease" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause yld rates males 
mx_ihd_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "IHD mortality rates difference males") +
  theme_classic()

print(mx_ihd_plot_compare_male)

##Select data from data frames for ihd mortality rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "ischemic heart disease" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "ischemic heart disease" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause yld rates females 
mx_ihd_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "IHD mortality rates difference females") +
  theme_classic()

print(mx_ihd_plot_compare_female)

##############################Prevalence rate ihd #############################################################

##Select data from data frames for ihd prevalence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "ischemic heart disease" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "ischemic heart disease" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates males 
px_ihd_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "IHD prevalence rates difference males") +
  theme_classic()

print(px_ihd_plot_compare_male)

##Select data from data frames for ihd prevalence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "ischemic heart disease" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "ischemic heart disease" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates females 
px_ihd_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "IHD prevalence rates difference females") +
  theme_classic()

print(px_ihd_plot_compare_female)

##############################Incidence rate ihd #############################################################

##Select data from data frames for ihd prevalence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "ischemic heart disease" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "ischemic heart disease" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates males 
ix_ihd_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "IHD incidence rates difference males") +
  theme_classic()

print(ix_ihd_plot_compare_male)

##Select data from data frames for ihd prevalence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "ischemic heart disease" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "ischemic heart disease" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates females 
ix_ihd_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "IHD incidence rates difference females") +
  theme_classic()

print(ix_ihd_plot_compare_female)

################ISCHEMIC STROKE
##############################Mortality rate ischemic stroke #############################################################

##Select data from data frames for ischemic stroke mortality rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "ischemic stroke" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "ischemic stroke" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot ischemic stroke mortality rates males

mx_is_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke mortality rates difference males") +
  theme_classic()

print(mx_is_plot_compare_male)

##Select data from data frames for ischemic stroke mortality rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "ischemic stroke" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "ischemic stroke" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot ischemic stroke mortality rates females 
mx_is_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality ischemic stroke")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke mortality rates difference females") +
  theme_classic()

print(mx_is_plot_compare_female)

##############################Prevalence rate ischemic stroke #############################################################

##Select data from data frames for ihd prevalence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "ischemic stroke" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "ischemic stroke" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates males 
px_is_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence IHD")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke prevalence rates difference males") +
  theme_classic()

print(px_is_plot_compare_male)

##Select data from data frames for ischemic stroke prevalence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "ischemic stroke" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "ischemic stroke" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates females 
px_is_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence ischemic stroke")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke prevalence rates difference females") +
  theme_classic()

print(px_is_plot_compare_female)

##############################Incidence rate ischemic stroke #############################################################

##Select data from data frames for ishcemic stroke incidence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "ischemic stroke" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "ischemic stroke" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates males 
ix_is_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence ischemic stroke")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke incidence rates difference males") +
  theme_classic()

print(ix_is_plot_compare_male)

##Select data from data frames for ischemic stroke incidence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "ischemic stroke" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "ischemic stroke" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot ischemic stroke incidence rates females 
ix_is_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence ischemic stroke")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke incidence rates difference females") +
  theme_classic()

print(ix_is_plot_compare_female)

################DIABETES MELLITUS
##############################Mortality rate diabetes mellitus #############################################################

##Select data from data frames for diabetes mellitus mortality rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "diabetes mellitus" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "diabetes mellitus" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot ischemic stroke mortality rates males

mx_DM_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality diabetes mellitus")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Diabetes mellitus mortality rates difference males") +
  theme_classic()

print(mx_DM_plot_compare_male)

##Select data from data frames for diabetes mellitus mortality rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "diabetes mellitus" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "diabetes mellitus" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot diabetes mellitus mortality rates females 
mx_DM_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality diabetes mellitus")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Diabetes mellitus mortality rates difference females") +
  theme_classic()

print(mx_DM_plot_compare_female)

##############################Prevalence rate diabetes mellitus #############################################################

##Select data from data frames for diabetes mellitus prevalence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "diabetes mellitus" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)
ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "diabetes mellitus" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates males 
px_DM_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence diabetes mellitus")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Diabetes mellitus prevalence rates difference males") +
  theme_classic()

print(px_DM_plot_compare_male)

##Select data from data frames for diabetes mellitus prevalence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "diabetes mellitus" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "diabetes mellitus" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates females 
px_DM_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence diabetes mellitus")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Ischemic stroke prevalence rates difference females") +
  theme_classic()

print(px_DM_plot_compare_female)

##############################Incidence rate diabetes mellitus #############################################################

##Select data from data frames for diabetes mellitus incidence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "diabetes mellitus" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "diabetes mellitus" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot incidence rate diabetes mellitus males 
ix_DM_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Diabetes mellitus")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Diabetes mellitus incidence rates difference males") +
  theme_classic()

print(ix_DM_plot_compare_male)

##Select data from data frames for diabetes mellitus incidence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "diabetes mellitus" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "diabetes mellitus" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot ischemic stroke incidence rates females 
ix_DM_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence diabetes mellitus")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Diabetes mellitus incidence rates difference females") +
  theme_classic()

print(ix_DM_plot_compare_female)

#####Breast cancer
##############################Mortality rate breast cancer #############################################################

##Select data from data frames for breast cancer mortality rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "breast cancer" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "breast cancer" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot breast cancer mortality rates females 
mx_BC_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality breast cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Breast cancer mortality rates difference females") +
  theme_classic()

print(mx_BC_plot_compare_female)

##############################Prevalence rate breast cancer #############################################################

##Select data from data frames for breast cancer prevalence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "breast cancer" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "breast cancer" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause prevalence rates females 
px_BC_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence breast cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Breast cancer prevalence rates difference females") +
  theme_classic()

print(px_BC_plot_compare_female)

##############################Incidence rate breast cancer #############################################################

##Select data from data frames for breast cancer incidence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "breast cancer" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "breast cancer" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot breast cancer incidence rates females 
ix_BC_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence breast cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Breast cancer incidence rates difference females") +
  theme_classic()

print(ix_BC_plot_compare_female)

################Colon and rectum cancer (DOSE RESPONSE FOR COLON CANCER?)
##############################Mortality rate colon and rectum cancer #############################################################

##Select data from data frames for colon and rectum cancer mortality rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "colon and rectum cancer" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "colon and rectum cancer" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot colon and rectum cancer mortality rates males

mx_CC_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality colon and rectum cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "colon and rectum cancer mortality rates difference males") +
  theme_classic()

print(mx_CC_plot_compare_male)

##Select data from data frames for colon and rectum cancer mortality rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "colon and rectum cancer" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "colon and rectum cancer" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot colon and rectum cancer mortality rates females 
mx_CC_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Mortality colon and rectum cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Colon and rectum cancers mortality rates difference females") +
  theme_classic()

print(mx_CC_plot_compare_female)

##############################Prevalence rate colon and rectum cancer #############################################################

##Select data from data frames for diabetes mellitus prevalence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "colon and rectum cancer" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)
ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "colon and rectum cancer" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot colon and rectum cancer prevalence rates males 
px_CC_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence colon and rectum cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "colon and rectum cancer prevalence rates difference males") +
  theme_classic()

print(px_CC_plot_compare_male)

##Select data from data frames for colon and rectum cancer prevalence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "colon and rectum cancer" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "colon and rectum cancer" & measure == "prevalence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot colon and rectum cancer prevalence rates females 
px_CC_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Prevalence colon and rectum cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Colon and rectum cancer prevalence rates difference females") +
  theme_classic()

print(px_CC_plot_compare_female)

##############################Incidence rate colon and rectum cancer #############################################################

##Select data from data frames for colon and rectum cancer incidence rates males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "colon and rectum cancer" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "colon and rectum cancer" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot incidence rate colon and rectum cancer males 
ix_CC_plot_compare_male <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Colon and rectum cancer incidence rate")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "colon and rectum cancer incidence rates difference males") +
  theme_classic()

print(ix_CC_plot_compare_male)

##Select data from data frames for colon and rectum cancer incidence rates females

ggplot_data_England <- filter(GBDEngland, sex == "female", cause == "colon and rectum cancer" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "female", cause == "colon and rectum cancer" & measure == "incidence") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot colon and rectum cancer incidence rates females 
ix_CC_plot_compare_female <- ggplot(ggplot_data_England, aes(age_cat,one_rate))+
  geom_line(aes(color = "England"))+
  geom_line(data=ggplot_data_GL,aes(color="Greater London"))+
  labs(colour="Locations",x="Age",y="Incidence colon and rectum cancer")+
  theme(legend.position = c(0, 1),legend.justification = c(0, 1))+
  scale_color_manual(values = c("blue","red")) +
  labs (title = "Colon and rectum cancer incidence rates difference females") +
  theme_classic()

print(ix_CC_plot_compare_female)
```

```{r, echo=FALSE}

plot(mx_plot_compare_male)
plot(mx_plot_compare_female)
plot(totalyld_plot_compare_male)
plot(totalyld_plot_compare_female)
plot(mx_ihd_plot_compare_male)
plot(mx_ihd_plot_compare_female)
plot(px_ihd_plot_compare_male)
plot(px_ihd_plot_compare_female)
plot(ix_ihd_plot_compare_male)
plot(ix_ihd_plot_compare_female)
plot(mx_is_plot_compare_male)
plot(mx_is_plot_compare_female)
plot(px_is_plot_compare_male)
plot(px_is_plot_compare_female)
plot(ix_is_plot_compare_male)
plot(ix_is_plot_compare_female)
plot(mx_DM_plot_compare_male)
plot(mx_DM_plot_compare_female)
plot(px_DM_plot_compare_male)
plot(px_DM_plot_compare_female)
plot(ix_DM_plot_compare_male)
plot(ix_DM_plot_compare_female)
plot(mx_CC_plot_compare_male)
plot(mx_CC_plot_compare_female)
plot(px_CC_plot_compare_male)
plot(px_CC_plot_compare_female)
plot(ix_CC_plot_compare_male)
plot(ix_CC_plot_compare_female)
plot(mx_BC_plot_compare_female)
plot(px_BC_plot_compare_female)
plot(ix_BC_plot_compare_female)
```

>>>>

```{r, echo=FALSE}
###TO DO: cubic splines for input rates

#in_data1: GBDEngland
#in_data2: GBDGL

sex <- c("male", "female")
cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancers", "breast cancer", "tracheal, bronchus, and lung cancer")
measure <- c("all causes", "ylds (years lived with disability)", "prevalence", "incidence")

for (i in sex){
  for (j in cause) {
    for (k in measure) {
      p <- paste("Plot", "compare", sex, cause, measure, sep = "_")
      assign(p, plot_GBD(in_data1 = GBDEngland, in_data2 = GBDGL, in_sex = sex, in_cause = cause, in_measure = measure))
      print(p)
    }
  }
}

```

```{r, echo=FALSE}
#Call plots here, add titles to figures

```
